---
title: "Simple Reserve Report Example"
author: "Andy Merlino"
date: "10/21/2014"
output: pdf_document
---
\begin{abstract}
I am going to display how a very simple reserve report could be created using R.  This document is only for display purposes.  It was created using data freely available on the CAS website.
\end{abstract}

\pagebreak

## Purpose

Ractuary has been requested by Nsure Ance Company (NAC) to provide a reserve estimate for their workers' compensation loss and loss alocated adjustment expense.  Losses are evaluated as of December 31, 1997... 

## Background

NAC began offering workers' compensation coverage in 1988.  Each policy is written on a calendar year basis (i.e. beginning January 1 and ending December 31).  NAC has never purchased reinsurense coverage...

## Other Stuff

\pagebreak

## Analysis

A summary of our estimated ultimate loss & ALAE and the indicated total outstanding loss & ALAE:

```{r packages_and_options, message = FALSE, warning = FALSE}
# CRAN packages
library(dplyr) # for manipulating data
library(ChainLadder) # reserving projections
library(pander) # make pretty tables

# Ractuary packages. Install with devtools::install_github("merlinoa/*")
library(exhibit) # default exhibits from ChainLadder package
library(casdata) # load in the data

# set pander table options
panderOptions('table.split.table', 125)
panderOptions('table.alignment.default', 'right')
```

```{r data}
# filter the data to be used in our projections
wkcomp$calendar <- wkcomp$AccidentYear + wkcomp$DevelopmentLag
state <- wkcomp[wkcomp$GRCODE == 1767 & wkcomp$calendar < 1999, ]
```

```{r summary, echo = FALSE}
latest <- filter(state, calendar == 1998) %>% 
  select(AccidentYear,
         CumPaidLoss_D,
         IncurLoss_D,
         EarnedPremNet_D)
names(latest) <- c("AccidentYear", "Paid", "Incurred", "Premium")
```

```{r paid_triangle, echo = FALSE}
paid_tri <- as.triangle(state, 
                        origin = "AccidentYear", 
                        dev = "DevelopmentLag",
                        value = "CumPaidLoss_D")

pander(exhibit(paid_tri, eformat = TRUE))

select <- c(2.7, 1.35, 1.55, 1.08, 1.05, 1.03, 1.025, 1.015, 
            1.013, 1.15)
paid_ata <- exhibit(ata(paid_tri), selection = select, 
                    tail_column = TRUE)
pander(eformat(paid_ata))
```

```{r}
paid_proj <- data.frame(latest[, 1:2], ldf = cumprod(rev(select)))
paid_proj <- mutate(paid_proj, 
                    Ultimate = Paid * ldf)
pander(eformat(paid_proj))
```