---
title: "Table with Footnotes"
author: "Andy Merlino"
date: "Monday, November 17, 2014"
output: pdf_document
---

Attempting to create a LaTeX table with good footnotes.  I need the table to be generated using an existing R package for generating LaTeX tables from R code.

### Create the table
```{r}
library(pander)

# an arbitrary example of a simple data frame
df <- data.frame("col.one" = c(1.1, 9.9, 2.3), "col.two" = c(4, 7, 8))
rownames(df) <- c("A", "B", "C")
```

When we create a table using R code there are several packages we can use generate the markdown and then the LaTeX code to create footnotes.  We want our table to look like this.

--------------------------------------------------
    &nbsp;         col.one           col.two   
-------------- ------------------ ----------------
    **A**            1.1               1.4        

    **B**            9.9               1.4        

    **C**            2.3               1.3        
--------------------------------------------------

[^1]: Random note a
[^2]: Random note b

\pagebreak

## The pander package
```{r}
# default print of the tabel
pander(df)
```


## The xtable package

```{r, results = "asis"}
library(xtable)

df_table <- xtable(df,label='tabbig', caption='Example of longtable')
names(df_table)[1] <- paste("col one",'footnote')
print(df_table, tabular.environment = 'longtable', floating=FALSE,
      sanitize.text.function = function(str) gsub("footnote","\\footnote{my tricky footnote !!}", str, fixed=TRUE))
```